Predicting solutions for the Military Flight and Maintenance Planning problem

### 2020-09-09 R/presentations/EDAA202003/presentation.Rmd

---
title: "Predicting solutions for the Military Flight and Maintenance Planning problem"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
    | \tiny (franco.peschiera@isae-supaero.fr)
date: "September, 2020"
output:
  xaringan::moon_reader:
    css: ["footer-header.css", "default"]
    self_contained: false
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    toc: true
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    includes:
        in_header: header.tex
editor_options: 
  chunk_output_type: console
---

@@

1. Problem.
2. State of the art.
1. Solving techniques.
2. Machine Learning.
2. Experiments.
3. Conclusions.

@@

* Mirage 2000 fleet.
* A single workshop to do the maintenance operations.
* Check type D (overhaul maintenances): 
  * every 5 years or 1000 flight hours and 
  * takes 4-6 months.
* Fleets of 15-60 aircraft.
* Planning horizons of 90 periods (= 7.5 years).

@@

@@

* A series of $j \in \mathcal{J}$ pre-scheduled missions are planned along a horizon divided into $t \in \mathcal{T}$ periods.
* Each mission requires a certain **number** $R_{j}$ of aircraft $i \in \mathcal{I}$ which it employs for $H_j$ **hours** in each period.
* The heterogeneous fleet requires recurrent preventive maintenance operations (**checks**).
* A check takes exactly $M^d$ periods and cannot be interrupted. There is a limited **capacity** for maintenances at each period.
* The objective is to **minimize the total number of checks** while **maximizing the status of the fleet** at the each period of the horizon.

@@

$a_{ijt_1t_2}$: mission $j$ is assigned to aircraft $i$ between $t_1$ and $t_2$.  
$m_{it_1t_2}$: aircraft $i$ starts a check in $t_1$ and another check in $t_2$.

@@

@@

* **Technique**: *Quantile regressions* to estimate upper and lower bounds.
* **Training**: 5000 small instances.
* **Input features**: 
  * mean flight demand per period,
  * total remaining flight hours at start (init), 
  * variance of flight demand, 
  * demand of special missions, 
  * number of period where flight demand is cut in two.
* **Output features**: mean distance between maintenances.

@@

```{r, echo=FALSE, out.width='100%', warning=FALSE}
knitr::include_graphics('calendar3.png')
```

>>>>

---
title: "Predicting solutions for the Military Flight and Maintenance Planning problem"
author: |
    | Franco Peschiera, Alain Haït, Olga Battaïa, Nicolas Dupin
    | \tiny (franco.peschiera@isae-supaero.fr)
date: "March, 2020"
output:
  xaringan::moon_reader:
    css: ["footer-header.css", "default"]
    self_contained: false
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
  slidy_presentation:
    css: ./../../../css/baobab_slidy.css
    incremental: yes
    footer: "ISAE-SUPAERO, Université de Toulouse, France"
    toc: true
  beamer_presentation:
    theme: "Berlin"
    toc: true
    slide_level: 2
    incremental: yes
    fig_height: 4
    includes:
        in_header: header.tex
editor_options: 
  chunk_output_type: console
---

@@

1. Problem.
1. Context.
1. Solving techniques.
2. Machine Learning.
2. Experiments.
3. Conclusions.

@@

* Mirage 2000 fleet.
* A single workshop to do the maintenance operations.
* Type D (big maintenances): 
  * every 5 years and 
  * take 4-6 months.
* Fleets of 15-60 aircraft.
* Planning horizons of 90 periods (= 7.5 years).

@@

### Predictive maintenance

.center[
**Predicting *when* aircraft will need a maintenance**.
]
--

* This is not what we do.
* We make maintenance plans for the whole fleet, taking into account maintenance needs.
* So, we use this data to make better maintenance plans.
* Nevertheless, we will predict *something* during this presentation.

@@

* A series of $j \in \mathcal{J}$ pre-scheduled missions are planned along a horizon divided into $t \in \mathcal{T}$ periods.
* Each mission requires a certain **number** $R_{j}$ of aircraft $i \in \mathcal{I}$ which it employs for $H_j$ **hours** in each period.
* The heterogeneous fleet requires recurrent preventive maintenance operations (**checks**).
* A check takes exactly $M^d$ periods and cannot be interrupted. There is a limited **capacity** for maintenances at each period.
* The objective is to **minimize the total number of checks** while **maximizing the status of the fleet** at the end of the horizon.

@@

good model + good solver = solution.

@@

### Distance between maintenances

```{r, echo=FALSE, out.width='100%', warning=FALSE}
knitr::include_graphics('calendar3.png')

.pull-left[
* The distance between maintenance has a maximum of $E^{M}$ periods.
* Depending on the instance, the optimal distance can be shorter.
* This distance conditions the total number of patterns to create.

.pull-right[
```{r, echo=FALSE, out.width='70%'}
imgs = c('hist_mean_dist_complete_IT000125_20190716.png')
knitr::include_graphics(imgs)
```
]

@@

.pull-left[
* **Technique**: *Quantile regressions* to estimate upper and lower bounds.
* **Training**: 5000 small instances.
* **Input features**: 
  * mean flight demand per period,
  * total remaining flight hours at start (init), 
  * variance of flight demand, 
  * demand of special missions, 
  * number of period where flight demand is cut in two.
* **Output features**: mean distance between maintenances.
]

@@

.pull-right[
```{r, echo=FALSE, out.width='100%'}
imgs = c('QuantReg_mean_consum_upper_mean_dist_complete_IT000125_20190716.png')
knitr::include_graphics(imgs)
```
]
